Solar wind prediction for the Solar Probe Plus orbit

### 2017-05-07 paperMVVB/sections/abstract.tex
some minor changes to text and figures 1,2,3,5and 9; additions to §7

\abstract
{In view of the planned near-Sun spacecraft mission Solar~Probe~Plus (SPP) the solar wind environment for its mission duration (2018--2025) and down to its intended closest perihelion (\num{9.86}~solar radii) is extrapolated using in situ data. This yet uncharted region is of special interest because the critical Alfvénic and sonic surfaces are believed to lie within and thus still part of the solar wind acceleration as well.}	%context
{We present an empirical solar wind model for the inner heliosphere which is derived from Helios and OMNI in situ data. The space probes Helios~1 and Helios~2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of \SIrange{0.29}{0.98}{\au}. The OMNI data set consists of multi-spacecraft intercalibrated in situ data from \SI{1}{\au}. This model is used together with sunspot number predictions to estimate the frequency distributions of major solar wind parameters SPP will encounter on its mission.}	%aims
{The model covers the solar wind's magnetic field strength and its plasma parameters proton density, velocity and temperature.
Their individual frequency distributions are represented with lognormal functions. In addition, we also consider the velocity distribution's bi-componental shape, consisting of a slower and a faster part. The model accounts for solar activity and for solar distance dependency by shifting of these lognormal distributions. We compile functional relations to solar activity by correlating and fitting the frequency distributions with the sunspot number (SSN), using almost five solar cycles of OMNI data. Further, based on the combined data set from both Helios probes, the parameters' frequency distributions are fitted over solar distance to obtain exponential dependencies. Combining both the solar cycle and the solar distance relations, we get a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic.}	%methods
{The inclusion of SSN predictions and the extrapolation to the SPP perihelion region enables us to estimate the solar wind environment at SPP's planned orbital positions during its mission time. The estimated solar wind values at SPP's nearest perihelion vary up to +-XX~\%, arising only from differing next solar cycle amplitude assumptions.}	%results
{}	%conclusions

>>>>

\abstract
{In view of the planned near-Sun spacecraft mission Solar~Probe~Plus (SPP) the solar wind environment for its mission duration (2018--2025) and down to its intended closest perihelion (\num{9.86}~solar radii) is extrapolated using in situ data. This yet uncharted region is of special interest because the critical Alfvénic and sonic surfaces are believed to lie within and thus still part of the solar wind acceleration as well.}	%context
{We present an empirical solar wind model for the inner heliosphere which is derived from Helios and OMNI in situ data. The space probes Helios~1 and Helios~2 flew in the 1970s and observed solar wind in the ecliptic within heliocentric distances of \SIrange{0.29}{0.98}{\au}. The OMNI data set consists of multi-spacecraft intercalibrated in situ data from \SI{1}{\au}. This model is used together with sunspot number predictions to estimate the frequency distributions of major solar wind parameters SPP will encounter on its mission.}	%aims
{The model covers the solar wind's magnetic field strength and its plasma parameters proton density, velocity and temperature.
Their individual frequency distributions are represented with lognormal functions. In addition, we also consider the velocity distribution's bi-componental shape, consisting of a slower and a faster part. The model accounts for solar activity and for solar distance dependency by shifting of these lognormal distributions. We compile functional relations to solar activity by correlating and fitting the frequency distributions with the sunspot number (SSN), using almost five solar cycles of OMNI data. Further, based on the combined data set from both Helios probes, the parameters' frequency distributions are fitted over solar distance to obtain exponential dependencies. Combining both the solar cycle and the solar distance relations, we get a simple dynamical solar wind model for the inner heliosphere, confined to the ecliptic.}	%methods
{The inclusion of SSN predictions and the extrapolation to the SPP perihelion region enables us to estimate the solar wind environment at SPP's planned orbital positions during its mission time. The estimated solar wind values at SPP's nearest perihelion vary up to +-XX~\%, arising only from differing amplitude assumptions for the next solar cycle.}	%results
{}	%conclusions

### 2017-05-07 paperMVVB/sections/content.tex
some minor changes to text and figures 1,2,3,5and 9; additions to §7

%difference to other models
There are many studies analyzing the solar wind dependence on solar activity and heliocentric distance with Helios data (\citet{Schwenn1983, Bougeret1984, Schwenn1990}, more cites...). They examine average values, additionally distinguishing between slow and fast wind. In this paper we instead look at the variations of the whole frequency distributions, consider solar activity and extrapolate these to the near-Sun region.\\

@@

@@

Again, the velocity gets a special treatment with the double lognormal distribution (\ref{eq:double_lognormal_fit_function}). It is known that slow and fast solar wind stream occurrence rates follow the solar cycle, but their magnitudes stay fairly stable (cite?). This time we keep the two velocity components' positions constant and vary instead their balance with the SSN:
\begin{align}
	c(ssn) &= c_a \cdot ssn + c_b\,.	\label{eq:balance_with_ssn}
\end{align}
The fit result (see Table~\ref{tab:ssn_fit_parameters}) is a model in which three years after solar cycle minimum (SSN of zero) the slow solar wind has a share of almost two-thirds and decreases further with increasing SSN (see Fig.~\ref{fig:Vdbl_SSN_ratio_e_plot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_e_plot.pdf}}
	\caption{Balance of slow to fast solar wind over the by 3~years lagged SSN. The yearly ratios (+) and their weighted linear fit (solid) are obtained from OMNI data with a threshold of \SI{400}{\km\per\s}. The error bars denote the SSN standard deviation and the relative weight from the yearly data coverage. The model's balance (\ref{eq:balance_with_ssn}) is obtained without a threshold (dashed).}
	\label{fig:Vdbl_SSN_ratio_e_plot}
\end{figure}
% 3 years after minimum (SSN of zero) the slow wind has its maximal share of 0.638(32). 3 years after maximum (SSN of 200) it has only a share of 0.278(37).\\
The ratio of slow to fast wind obtained from yearly OMNI data via simply applying the commonly used constant velocity threshold of \SI{400}{\km\per\s} (cite?) has a flatter SSN dependence than the model's balance. Why?\\
Both should not necessary be identical, because there is no specific velocity threshold between slow and fast solar wind types, as the velocity ranges of both types overlap (cite?).\\

@@

%exponential fitting
%%%%%%%%%%%%%%%%%%%%
\section{Solar distance dependency}
\label{sec:solar_distance_dependency}

In this section we use Helios data to obtain exponential fit functions for the heliocentric distance dependency and evaluate the fits' extrapolation behavior in direction to the Sun. To fit the bulk solar wind distributions' distance dependency we use the frequency fitting method from Sect.~\ref{sec:frequency_distribution} on distance-binned Helios data. This results in models comprising of exponentially with distance shifted lognormal functions.

%Helios data
\subsection{Helios distance data}
\label{sec:helios_distance_data}

The Helios probes were the only spacecraft measuring in situ solar wind over large solar distance ranges in the inner heliosphere. We use the combined data from both Helios~1 and Helios~2 probes. Helios~1's (Helios~2's) highly elliptical orbit in the ecliptic covered a solar distance range of \SIrange{0.31}{0.98}{\au} (\SIrange{0.29}{0.98}{\au}). Launched during solar cycle minimum, the data of both probes cover the rise to the maximum of cycle 21 ($\sim$6.5~years at varying distances).

@@

Naturally, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$. The additional fit parameters are the balancing parameter $c$ and from the second lognormal part $a_\text{med,2}$ and $a_\text{avg,2}$. The resulting fit coefficients for the four solar wind parameters are presented in Table~\ref{tab:extrapolation_model_fit_parameters}.
\begin{table*}
	\caption{These are the resulting fit coefficients with the single lognormal exponential function, respectively double lognormal for the velocity. The errors in brackets are the estimated standard deviations of each fit parameter.}
	\label{tab:extrapolation_model_fit_parameters}
	\centering
	\sisetup{table-figures-integer=1, table-figures-decimal=3, table-figures-exponent=0}
	\begin{tabular}{l c
	S[table-format = 1.3(2), table-space-text-post = a, table-align-text-post = false]
	S[table-format = 1.3(2), table-space-text-post = a, table-align-text-post = false]
	S[table-format = +1.4(2)]
	S[table-format = 1.3(2)]}
		\hline\hline
		\multicolumn{2}{c}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Exponent}	&\multicolumn{1}{c}{Balance}\\
			&	&\multicolumn{1}{c}{$a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$a_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b$}	&$c$\\
		\hline
		\multicolumn{2}{l}{Magnetic field}	&5.358(25)	&5.705(28)	&-1.662(11)	&\multicolumn{1}{c}{--}\\
		\multicolumn{2}{l}{Density}	&5.424(33)	&6.845(47)	&-2.114(20)	&\multicolumn{1}{c}{--}\\
		\multicolumn{2}{l}{Temperature}	&6.357(64)	&10.72(14)	&-1.100(20)	&\multicolumn{1}{c}{--}\\
		\hline
		\multirow{1}{*}{Velocity}	&$W''_1$	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}	&\multirow{2}{*}{0.557(45)}\\
			&$W''_2$	&5.26(13)	&5.42(11)	&	&\\
		\cline{2-6}
		\multicolumn{2}{r}{$W''_\text{II}$}	&4.35(13)\tablefootmark{b}	&4.77(11)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{Values in their respective units \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
		\tablefoottext{b}{Velocity median and mean \SI{1}{\au} values for the resulting function. Error estimates derived from the individual fit part errors.}
	}
\end{table*}

@@

model errors, maximum errors\\
The extreme values of the velocity and temperature seem to be too high (adjust color scale...)\\
L-> high value plots... (refer to histogram zoom in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot})\\

@@

to get the combined model function $W''(x,ssn,r)$. And for the velocity $W_{II}''(x,ssn,r)$ with the double lognormal function.\\

%model errors
give model errors sizes/uncertainties (sigmas); $W''_\text{err}(x,ssn,r)$, $x_\text{med\_err}(ssn,r)$

@@

\section{Model extrapolation to SPP orbital time and position}
To estimate the solar wind environment at SPP's planned orbital positions during its mission time, SSN predictions and extrapolations to the SPP perihelion region are included into the general solar wind model.\\

%SPP orbit
SPP orbit description, Venus flybys, within ecliptic, \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_c_plot})\\

\subsection{SPP mission time frame/SSN prediction}
%SSN prediction
choosing SSN prediction sources as input:\\
SIDC prediction---12-month forecast (Kalman fiter combined method)\\
The SWPC prediction (until end of current cycle/end of 2019) follows a consensus of the Solar~Cycle~24 Prediction~Panel.\\
For the prediction of the next solar cycle we simply assume a course similar to the last and thus we simply shift the last cycle by 11~years. Additionally we consider the two alternatives of half and twice the amplitude.\\
SIDC + SWPC + previous cycle~24 (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_c_plot})\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_c_plot.pdf}}
	\caption{SPP's solar distance during its mission time (top). Consecutive Venus flybys bring its perihelia nearer to the Sun. Actual and predicted SSN (bottom), i.e. SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and simply shifted SSN from previous cycle~24, together with two alternative trends of half and twice the amplitude.}
	\label{fig:SPP_orbit_predicted_SSN_overview_c_plot}
\end{figure}

=> Implications for the mission...\\

@@

\subsection{SPP orbit/near-Sun extrapolation}
The extrapolation distance is only about one third of the model range, but as the parameters follow exponential change, one has to look at the logarithmic distance which is indeed one and a half times the model range.\\

@@

The near-Sun (SPP perihelion) solar wind velocity is expected to be slower than our model estimates, because the position of the source (Alfvénic critical) surface is predicted to lie between 15--30~Rs (Schatten1969, Sittler1999, Exarhos2000, Katsikas2010, Goelzer2014; choose references...), up to which the solar wind is believed to be accelerated.\\

@@

Comparison with existing near-Sun models (renew extrapolation figure to 1-column):\\

@@

\subsection{SPP solar wind model}
Implementing the orbital distance data and predicted SSN for the mission time we get SPP's estimated solar wind environment.\\
A zoom into the first and the nearest perihelia shows... (Figs.~\ref{fig:SPP_perihelia_prediction_c_plot} and \ref{fig:SPP_perihelia_prediction_nearest_c_plot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_c_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's first perihelion in 2018. For the velocity the SSN independent slow and fast parts are plotted.}
	\label{fig:SPP_perihelia_prediction_c_plot}
\end{figure}
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_c_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's nearest perihelion in 2024. For the velocity the SSN independent slow and fast parts are plotted.}
	\label{fig:SPP_perihelia_prediction_nearest_c_plot}
\end{figure}

@@

The use of hourly data instead of higher resolution data (less than 1~min) has no significant influence on the bulk results. The minutely OMNI data frequency distributions are almost congruent and differ only slightly at their extreme ends.\\
The many hourly Helios data points which contain only a few measurements, contribute with a larger scatter to the frequency distributions \citep[p.~491]{Schwenn1983}.\\

@@

OMNI data is not corrected for solar distace. only available for 1-/5-min data\\

@@

Further investigations should be done into structure extrapolations, outward extension of model to Mars...\\

>>>>

%difference to other models
There are many studies analyzing the solar wind dependence on solar activity and heliocentric distance with Helios data (\citet{Schwenn1983, Bougeret1984, Schwenn1990}, more cites?). They examine average values, additionally distinguishing between slow and fast wind. In this paper we instead look at the variations of the whole frequency distributions, consider solar activity and extrapolate these to the near-Sun region.\\

@@

%hourly data
We note that the use of higher time resolution instead, would not significantly change our results. The frequency distributions of the also available minutely OMNI data set are almost congruent with the hourly---they only differ slightly at their extreme ends.

@@

Again, the velocity gets a special treatment with the double lognormal distribution (\ref{eq:double_lognormal_fit_function}). It is known that slow and fast solar wind stream occurrence rates follow the solar cycle, but their magnitudes stay fairly stable (cite?). This time we keep the two velocity components' positions constant and vary instead their balance with the SSN:
\begin{align}
	c(ssn) &= c_a \cdot ssn + c_b\,.	\label{eq:balance_with_ssn}
\end{align}
The fit result (see Table~\ref{tab:ssn_fit_parameters}) is a model in which three years after solar cycle minimum (SSN of zero) the slow solar wind has a share of almost two-thirds and decreases further with increasing SSN (see Fig.~\ref{fig:Vdbl_SSN_ratio_e_plot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_e_plot.pdf}}
	\caption{Balance of slow to fast solar wind over the by 3~years lagged SSN. The yearly ratios (+) and their weighted linear fit (solid) are obtained from OMNI data with a threshold velocity of $v_\text{th} = \SI{400}{\km\per\s}$. The error bars denote the SSN standard deviation and the relative weight from the yearly data coverage. The model's balance (\ref{eq:balance_with_ssn}) is obtained without a threshold (dashed).}
	\label{fig:Vdbl_SSN_ratio_e_plot}
\end{figure}
% 3 years after minimum (SSN of zero) the slow wind has its maximal share of 0.638(32). 3 years after maximum (SSN of 200) it has only a share of 0.278(37).\\
The ratio of slow to fast wind obtained from yearly OMNI data via simply applying the commonly used constant velocity threshold of $v_\text{th} = \SI{400}{\km\per\s}$ (cite?) has a flatter SSN dependence than the model's balance. Why?\\
Both should not necessary be identical, because there is no specific velocity threshold between slow and fast solar wind types, as the velocity ranges of both types overlap (cite?).\\

@@

%exponential fitting
%%%%%%%%%%%%%%%%%%%%
\section{Solar distance dependency}
\label{sec:solar_distance_dependency}
In this section we use Helios data to obtain exponential fit functions for the heliocentric distance dependency and also evaluate the fits' extrapolation behavior in direction to the Sun. To fit the bulk solar wind distributions' distance dependency we use the frequency fitting method from Sect.~\ref{sec:frequency_distribution} on distance-binned Helios data. This results in models comprising of exponentially with distance shifted lognormal functions.

%Helios data
\subsection{Helios distance data}
\label{sec:helios_distance_data}
The Helios probes were the only spacecraft measuring in situ solar wind over large solar distance ranges in the inner heliosphere. We use the combined data from both Helios~1 and Helios~2 probes. Helios~1's (Helios~2's) highly elliptical orbit in the ecliptic covered a solar distance range of \SIrange{0.31}{0.98}{\au} (\SIrange{0.29}{0.98}{\au}). Launched during solar cycle minimum, the data of both probes cover the rise to the maximum of cycle 21 ($\sim$6.5~years at varying distances).

%hourly data
Again we choose data with hourly resolution to allow its use along with the hourly OMNI data. As \citet{Schwenn1983} pointed out, the many hourly Helios data points which contain only a few measurements, contribute with a larger scatter to the frequency distributions, nevertheless their effect is insignificant in the treatment of the bulk data.	%\citet[p.~491]{Schwenn1983}

@@

Naturally, we use the double lognormal function~(\ref{eq:double_lognormal_fit_function}) for the velocity distribution fit, resulting in $W''_\text{II}(x,r)$. The additional fit parameters are the balancing parameter $c$ and from the second lognormal part $a_\text{med,2}$ and $a_\text{avg,2}$. The resulting fit coefficients for the four solar wind parameters are presented in Table~\ref{tab:extrapolation_model_fit_parameters}.
\begin{table*}
	\caption{These are the resulting fit coefficients with the single lognormal exponential function, respectively double lognormal for the velocity. The errors in brackets are the estimated standard deviations of each fit parameter.}
	\label{tab:extrapolation_model_fit_parameters}
	\centering
	\sisetup{table-figures-integer=1, table-figures-decimal=3, table-figures-exponent=0}
	\begin{tabular}{l c
	S[table-format = 1.3(2), table-space-text-post = a, table-align-text-post = false]
	S[table-format = 1.3(2), table-space-text-post = a, table-align-text-post = false]
	S[table-format = +1.4(2)]
	S[table-format = 1.3(2)]}
		\hline\hline
		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Exponent}	&\multicolumn{1}{c}{Balance}\\
			&	&\multicolumn{1}{c}{$a_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$a_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$b$}	&$c$\\
		\hline
		\multicolumn{2}{l}{Magnetic field}	&5.358(25)	&5.705(28)	&-1.662(11)	&\multicolumn{1}{c}{--}\\
		\multicolumn{2}{l}{Density}	&5.424(33)	&6.845(47)	&-2.114(20)	&\multicolumn{1}{c}{--}\\
		\multicolumn{2}{l}{Temperature}	&6.357(64)	&10.72(14)	&-1.100(20)	&\multicolumn{1}{c}{--}\\
		\hline
		\multirow{1}{*}{Velocity}	&$W''_1$	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}	&\multirow{2}{*}{0.557(45)}\\
			&$W''_2$	&5.26(13)	&5.42(11)	&	&\\
		\cline{2-6}
		\multicolumn{2}{r}{$W''_\text{II}$}	&4.35(13)\tablefootmark{b}	&4.77(11)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{Values in their respective units \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
		\tablefoottext{b}{Velocity median and mean \SI{1}{\au} values for the resulting function. Error estimates derived from the individual fit part errors.}
	}
\end{table*}

@@

model errors, maximum errors\\
The extreme values of the velocity and temperature seem to be too high\\
L-> high value plots... (refer to histogram zoom in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot})\\

@@

to get the combined model function $W''(x,ssn,r)$. And for the velocity $W_\text{II}''(x,ssn,r)$ with the double lognormal function.\\

%model errors
give model errors sizes/uncertainties (sigmas); $W''_\text{err}(x,ssn,r)$, $x_\text{med\_err}(ssn,r)$\\

@@

\section{Model extrapolation to SPP orbital time and position}
To estimate the solar wind environment at SPP's planned orbital positions during its mission time, SSN predictions are included into the general solar wind model and extrapolations to the SPP perihelion region are performed.\\

\subsection{SSN prediction for SPP mission time}
%SSN prediction
For the SSN prediction there are several sources available. The SIDC provides 12-month SSN forecasts\footnote{\url{http://sidc.be/silso/forecasts}} obtained from different methods (e.g. Kalman filter combined method) (use cite...). The Space Weather Prediction Center's (SWPC) prediction follows a consensus of the Solar~Cycle~24 Prediction~Panel\footnote{\url{http://legacy-www.swpc.noaa.gov/SolarCycle/}} (until end of 2019) (use cite...).

For the prediction of the next solar cycle~25 we simply assume a course similar to the last and thus we shift the last cycle by 11~years. Additionally we consider the two alternatives of half and twice its amplitude. The SSN for SPP's first perihelion will be small---certainly below 20, whereas its nearest perihelia, which commence at the height of cycle~25, will have as of now almost unpredictable SSN amplitudes (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_d_plot})\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_predicted_SSN_overview_d_plot.pdf}}
	\caption{SPP's solar distance during its mission time (top). Consecutive Venus flybys bring its perihelia nearer to the Sun. Actual and predicted SSN (bottom), i.e. SIDC 13-month smoothed monthly actual SSN, SIDC prediction, SWPC prediction and simply by 11~years shifted SSN from previous cycle~24, together with two alternative trends of half and twice its amplitude.}
	\label{fig:SPP_orbit_predicted_SSN_overview_d_plot}
\end{figure}

[=> Implications for the mission...]\\

prediction errors...\\

\subsection{Near-Sun extrapolation for SPP orbit}

%SPP orbit
SPP orbit description, Venus flybys, within ecliptic, \citep{Fox2015}, (see Fig.~\ref{fig:SPP_orbit_predicted_SSN_overview_d_plot})\\

@@

The extrapolation distance is only about one third of the model range, but as the parameters follow exponential change, one has to look at the logarithmic distance which is indeed one and a half times the model range.\\

@@

The near-Sun (SPP perihelion) solar wind velocity is expected to be slower than our model's estimates, because the position of the source (Alfvénic critical) surface is predicted to lie between 15--30~Rs (Schatten1969, Sittler1999, Exarhos2000, Katsikas2010, Goelzer2014; choose references...), up to which the solar wind is believed to be accelerated.\\

@@

Comparison with existing near-Sun models (renew extrapolation figure to 1-column; with half/twice SSN)\\
calculate or set min, avg and max SSN (e.g. 0, 100, 200)\\

@@

\subsection{SPP solar wind environment estimation}
Implementing the orbital distance data and predicted SSN for the mission time we get SPP's estimated solar wind environment.\\
The zoom into the first and the nearest perihelia show which solar wind parameter magnitudes can be expected there (Figs.~\ref{fig:SPP_perihelia_prediction_c_plot} and \ref{fig:SPP_perihelia_prediction_nearest_c_plot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_c_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's first perihelion in 2018 at ?\SI{0.16}{\au}. For the velocity the SSN independent slow and fast parts are plotted.}
	\label{fig:SPP_perihelia_prediction_c_plot}
\end{figure}
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_c_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black) and their error bands (grey) during SPP's nearest perihelion in 2024 at \SI{0.0459}{\au}. For the velocity the SSN independent slow and fast parts are plotted.}
	\label{fig:SPP_perihelia_prediction_nearest_c_plot}
\end{figure}

@@

@@

%OMNI data is not corrected for solar distace. only available for 1-/5-min data\\

@@

Further investigations should be done into structure extrapolations; outward extension of model to Mars seems feasable...\\
